### 2019-09-09 papers/journal/2019_ACTA_Rebuttal_Rd2.txt

  Pt #3: 
-------- Handle by Ashutosh --------------   
  Another point that should be revised further is around 
  clarifying the contributions of this paper. The response 
  document summarizes nicely that, together with additional 
  QBF encoding, "this paper brings together all the results 
  with extended experiments and more detailed expositions for 
  the benefit of both biological and computation community." 
  However, I did not find a similar concise statement of the 
  contributions in the text. In addition, some of the stated 
  advances over previous approaches seem incremental and minor. 
  For example, for the previous CBMC-based method it is stated 
  that "...the scalability of the method was insufficient. 
  The tool was able to handle the system with just eight 
  compartments". Yet, we learn that "A typical eukaryotic 
  cell contains 9 organelles" and even one of the methods 
  presented in this paper fails for some of the experimental 
  evaluations with 7 or more compartments. The contributions 
  of this work, perhaps in the integration and evaluation of
  several methods reported previously, should be stated clearly 
  and accurately in the main text.

  > A final minor point is about the use of "Synthesis" as 
    an encoding in Fig 4 and the relevant explanations. 
    Since the other problems list verification techniques 
    and solvers (e.g. BMC, SMT, QBF) and no novel synthesis 
    algorithms were developed for this problem, it would be 
    more appropriate to specify QBF as the encoding used for 
    the "VTS synthesis" problem.

  Authors response: We have now incorporated this information 
  in Fig 4.

### 2019-09-09 papers/journal/problem.tex
related work

		\begin{forest}
			/tikz/every node/.append style={font=\sffamily,minimum size=1.0cm},
			for tree={
				edge+={->,thick},% uncomment for arrows
				draw,
				rounded corners,
				node options={align=center,},
				text width=1.7cm,
				calign=fixed edge angles, calign primary angle=-84,calign secondary angle=85,
				%	anchor=center,	
				%	calign=center,
			},
			where level=0{%
				parent anchor=children,
			}{%
				folder,
				grow'=0,
				if level=1{% this changes the edges from level 0 to nodes at level 1
					before typesetting nodes={child anchor=north},
					edge path'={(!u.parent anchor) -- ++(0,-5pt) -| (.child anchor)},
				}{},
			}
			[\textbf{VTS Search \\ Problems}, fill=white!20, parent, s sep=1mm,
			[\textbf{1.Existential Condition}, for tree={fill=fv, child}, 
			[BMC, for tree={fill=ai, child}]
			[SMT, for tree={fill=ai, child}]
			]
			[\textbf{2.Universal Condition}, for tree={fill=fv, child},
			[QBF, for tree={fill=ai, child}]
			]
			[\textbf{3.VTS Synthesis}, for tree={fill=fv,child}, 
			[Synthesis, for tree={fill=ai, child}]
			]
			]
		\end{forest}
	}
\end{adjustbox}
\vspace{0.01cm}

>>>>

		\begin{forest}
			/tikz/every node/.append style={font=\sffamily,minimum size=1.0cm},
			for tree={
				edge+={->,thick},% uncomment for arrows
				draw,
				rounded corners,
				node options={align=center,},
				text width=1.7cm,
				calign=fixed edge angles, calign primary angle=-84,calign secondary angle=85,
				%	anchor=center,	
				%	calign=center,
			},
			where level=0{%
				parent anchor=children,
			}{%
				folder,
				grow'=0,
				if level=1{% this changes the edges from level 0 to nodes at level 1
					before typesetting nodes={child anchor=north},
					edge path'={(!u.parent anchor) -- ++(0,-5pt) -| (.child anchor)},
				}{},
			}
			[\textbf{VTS Search \\ Problems}, fill=white!20, parent, s sep=1mm,
			[\textbf{1.Existential Condition}, for tree={fill=fv, child}, 
			[BMC, for tree={fill=ai, child}]
			[SMT, for tree={fill=ai, child}]
			]
			[\textbf{2.Universal Condition}, for tree={fill=fv, child},
			[QBF, for tree={fill=ai, child}]
			]
			[\textbf{3.VTS Synthesis}, for tree={fill=fv,child}, 
			[Synthesis (QBF), for tree={fill=ai, child}]
			]
			]
		\end{forest}
	}
\end{adjustbox}
\vspace{0.01cm}

### 2019-09-09 papers/journal/related.tex
related work

There has been some work in applying synthesis technique in biology. %especially in gene regulatory networks~\cite{shavit2016automated, fisher2015synthesising}. 
A recent work by \cite{fisher2015synthesising} synthesize executable gene regulatory networks from single-cell gene expression data.
%
In \cite{shavit2016automated} synthesis of switching GRN (with changing topology) is performed.
%
The~\cite{fisher2015synthesising} uses constraint (satisfiability) solving techniques whereas \cite{shavit2016automated} uses SMT to perform synthesis. 
%
Synthesis technique is also used in optimal synthesis for chemical reaction networks~\cite{cardelli2017syntax}.
%
%
The work
%The paper \cite{cardelli2017syntax} in addition to using SMT over  ODE, 
use a template-guided approach in addition to using SMT over ODE. In our case queries contain quantifiers so we have employed QBF solving with Z3 for solving the synthesis problem. 
%
To our best knowledge, this is the first application of synthesis in VTS.
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

>>>>

There has been some work in applying synthesis technique in biology. 
%
Recent work by \cite{fisher2015synthesising} synthesize executable gene regulatory networks from single-cell gene expression data.
%
In \cite{shavit2016automated} synthesis of switching GRN (with changing topology) is performed.
%
The~\cite{fisher2015synthesising} uses constraint (satisfiability) solving techniques whereas \cite{shavit2016automated} uses SMT to perform synthesis. 
%
Synthesis technique is also used in optimal synthesis for chemical reaction networks~\cite{cardelli2017syntax}.
%
%
The work uses a template-guided approach in addition to using SMT over ODE. In our case, queries contain quantifiers so we have employed QBF solving with Z3 for solving the synthesis problem. 
%
To our best knowledge, this is the first application of synthesis in VTS.
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
